---
title: "AGHW7"
author: "AG"
date: "2023-03-28"
output: html_document
---
## REPO: https://github.com/bobagh/AGHWs
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
install.packages("rmarkdown", repos = "https://packagemanager.rstudio.com/all/latest")
```
```{r}
#install.packages("contrib.url")
```

```{r}
library(tidyverse)
library(productplots)
library(ggplot2)
```
```{r}
data(happy, package = "productplots")
head(happy)
```

```{r}
#install.packages("readr")
# Load the readr package to read in the data
library(readr)

# Use the readRDS function to read in the data from the raw.githubusercontent.com URL
HAPPY <- readRDS(url("https://raw.githubusercontent.com/bobagh/AGHWs/main/HAPPY.rds"))

# View the data
head(HAPPY)

```
```{r}
# Set NULLS
HAPPY$HAPPY <- replace(HAPPY$HAPPY, (HAPPY$HAPPY == "IAP"), NA)
HAPPY$HAPPY <- replace(HAPPY$HAPPY, (HAPPY$HAPPY == "DK"), NA)
HAPPY$HAPPY <- replace(HAPPY$HAPPY, (HAPPY$HAPPY == "NA"), NA)
# SET TYPES
HAPPY$HAPPY <- as.factor(HAPPY$HAPPY)
# SET FACTOR ORDER
HAPPY$HAPPY <- factor(HAPPY$HAPPY, levels = c("NOT TOO HAPPY","PRETTY HAPPY", "VERY HAPPY"))
```

```{r}
# SET NULLS
HAPPY$AGE <- replace(HAPPY$AGE, (HAPPY$AGE == "IAP"), NA)
HAPPY$AGE <- replace(HAPPY$AGE, (HAPPY$AGE == "AGE"), NA)
HAPPY$AGE <- replace(HAPPY$AGE, (HAPPY$AGE == "AGE"), NA)
# SET TYPES
HAPPY$AGE <- replace(HAPPY$AGE, (HAPPY$AGE == "89 OR OLDER"), 89)
HAPPY$AGE <- as.numeric(HAPPY$AGE)
```

```{r}
# Set NULLS
HAPPY$YEAR <- replace(HAPPY$YEAR, (HAPPY$YEAR == "IAP"), NA)
HAPPY$YEAR <- replace(HAPPY$YEAR, (HAPPY$YEAR == "DK"), NA)
HAPPY$YEAR <- replace(HAPPY$YEAR, (HAPPY$YEAR == "NA"), NA)
# SET TYPES
HAPPY$YEAR <- as.numeric(HAPPY$YEAR)
```

```{r}
# Set NULLS
HAPPY$SEX <- replace(HAPPY$SEX, (HAPPY$SEX == "IAP"), NA)
HAPPY$SEX <- replace(HAPPY$SEX, (HAPPY$SEX == "DK"), NA)
HAPPY$SEX <- replace(HAPPY$SEX, (HAPPY$SEX == "NA"), NA)
# SET TYPES
HAPPY$SEX <- as.factor(HAPPY$SEX)
```

```{r}
HAPPY$MARITAL <- replace(HAPPY$MARITAL, (HAPPY$MARITAL == "IAP"), NA)
HAPPY$MARITAL <- replace(HAPPY$MARITAL, (HAPPY$MARITAL == "DK"), NA)
HAPPY$MARITAL <- replace(HAPPY$MARITAL, (HAPPY$MARITAL == "NA"), NA)
# SET TYPES
HAPPY$MARITAL <- as.factor(HAPPY$MARITAL)
```

```{r}
HAPPY$DEGREE <- replace(HAPPY$DEGREE, (HAPPY$DEGREE == "IAP"), NA)
HAPPY$DEGREE <- replace(HAPPY$DEGREE, (HAPPY$DEGREE == "DK"), NA)
HAPPY$DEGREE <- replace(HAPPY$DEGREE, (HAPPY$DEGREE == "NA"), NA)
# SET TYPES
HAPPY$DEGREE <- as.factor(HAPPY$DEGREE)
```

```{r}
# Set NULLS
HAPPY$FINRELA <- replace(HAPPY$FINRELA, (HAPPY$FINRELA == "IAP"), NA)
HAPPY$FINRELA <- replace(HAPPY$FINRELA, (HAPPY$FINRELA == "DK"), NA)
HAPPY$FINRELA <- replace(HAPPY$FINRELA, (HAPPY$FINRELA == "NA"), NA)
# SET TYPES
HAPPY$FINRELA <- as.factor(HAPPY$FINRELA)
# SET FACTOR ORDER
HAPPY$FINRELA <- factor(HAPPY$FINRELA, levels = c("FAR BELOW AVERAGE", "BELOW AVERAGE", "AVERAGE", "ABOVE AVERAGE", "FAR ABOVE AVERAGE"))
```

```{r}
# Set NULLS
HAPPY$HEALTH <- replace(HAPPY$HEALTH, (HAPPY$HEALTH == "IAP"), NA)
HAPPY$HEALTH <- replace(HAPPY$HEALTH, (HAPPY$HEALTH == "DK"), NA)
HAPPY$HEALTH <- replace(HAPPY$HEALTH, (HAPPY$HEALTH == "NA"), NA)
# SET TYPES
HAPPY$HEALTH <- as.factor(HAPPY$HEALTH)
# SET FACTOR ORDER
HAPPY$HEALTH <- factor(HAPPY$HEALTH, levels = c("POOR", "FAIR", "GOOD", "EXCELLENT"))
```

```{r}
# SET NULLS
HAPPY$WTSSALL <- replace(HAPPY$WTSSALL, (HAPPY$WTSSALL == "IAP"), NA)
HAPPY$WTSSALL <- replace(HAPPY$WTSSALL, (HAPPY$WTSSALL == "AGE"), NA)
HAPPY$WTSSALL <- replace(HAPPY$WTSSALL, (HAPPY$WTSSALL == "AGE"), NA)
# SET TYPES
HAPPY$WTSSALL <- as.numeric(HAPPY$WTSSALL)
```

# Part Two:
___
```{r}
library(ggplot2)
ggplot(HAPPY, aes(x = MARITAL, fill = SEX)) +
  geom_bar(position = "fill") +
  labs(x = "Marital status", y = "Proportion", fill = "Sex") +
  theme_bw()
```

```{r}
ggplot(HAPPY) +
  geom_bar(aes(x=SEX, fill=MARITAL),
           position = "dodge") +
  facet_wrap(~HAPPY)
```
The facet_wrap function creates a grid of plots, with each plot showing a different subset of the data based on the HAPPY variable. This function splits the data into panels, with each panel displaying a different level of the HAPPY variable. This is useful when you want to explore how the relationship between SEX and MARITAL varies across different levels of HAPPY.

Overall, this plot is a useful way to visualize the relationship between SEX and MARITAL in the HAPPY data frame, while also showing how this relationship varies across different levels of the HAPPY variable.

# Individual Question: Ahmed Gharib
___
### Is there a relation between age and Marital states?
```{r}
ggplot(HAPPY) +
  geom_bar(aes(x=AGE, fill= MARITAL),
           position = "dodge") +
  facet_wrap(~MARITAL)
```
The facet_wrap function creates a grid of plots, with each plot showing a different subset of the data based on the MARITAL variable. This function splits the data into panels, with each panel displaying a different level of the MARITAL variable. This is useful when you want to explore how the relationship between AGE and MARITAL varies across different levels of MARITAL.

Overall, this plot is a useful way to visualize the relationship between AGE and MARITAL in the HAPPY data frame, while also showing how this relationship varies across different levels of the MARITAL variable. By comparing the different panels, you can get a sense of whether the relationship between AGE and MARITAL differs across the different levels of MARITAL. For example, you can see whether there are any differences in the distribution of ages for different marital status groups.