---
title: "AGHW7"
author: "AG"
date: "2023-03-28"
output: html_document
---
## REPO: https://github.com/bobagh/AGHWs
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
install.packages("productplots")
```
```{r}
install.packages("readr")
```

```{r}
library(tidyverse)
library(productplots)
library(ggplot2)
```
```{r}
data(happy, package = "productplots")
head(happy)
```

```{r}
# Load the readr package to read in the data
library(readr)

# Set the URL of the raw file on GitHub
url <- ("https://github.com/bobagh/AGHWs/blob/main/HAPPY.rds")

# Use the readRDS function to read in the data
HAPPY <- readRDS(url)

# View the data
head(HAPPY)

```
```{r}
# Set NULLS
HAPPY$HAPPY <- replace(HAPPY$HAPPY, (HAPPY$HAPPY == "IAP"), NA)
HAPPY$HAPPY <- replace(HAPPY$HAPPY, (HAPPY$HAPPY == "DK"), NA)
HAPPY$HAPPY <- replace(HAPPY$HAPPY, (HAPPY$HAPPY == "NA"), NA)
# SET TYPES
HAPPY$HAPPY <- as.factor(HAPPY$HAPPY)
# SET FACTOR ORDER
HAPPY$HAPPY <- factor(HAPPY$HAPPY, levels = c("NOT TOO HAPPY","PRETTY HAPPY", "VERY HAPPY"))
```
```{r}
# SET NULLS
HAPPY$AGE <- replace(HAPPY$AGE, (HAPPY$AGE == "IAP"), NA)
HAPPY$AGE <- replace(HAPPY$AGE, (HAPPY$AGE == "AGE"), NA)
HAPPY$AGE <- replace(HAPPY$AGE, (HAPPY$AGE == "AGE"), NA)
# SET TYPES
HAPPY$AGE <- replace(HAPPY$AGE, (HAPPY$AGE == "89 OR OLDER"), 89)
HAPPY$AGE <- as.numeric(HAPPY$AGE)
```
```{r}
# Set NULLS
HAPPY$YEAR <- replace(HAPPY$YEAR, (HAPPY$YEAR == "IAP"), NA)
HAPPY$YEAR <- replace(HAPPY$YEAR, (HAPPY$YEAR == "DK"), NA)
HAPPY$YEAR <- replace(HAPPY$YEAR, (HAPPY$YEAR == "NA"), NA)
# SET TYPES
HAPPY$YEAR <- as.numeric(HAPPY$YEAR)
```
```{r}
# Set NULLS
HAPPY$SEX <- replace(HAPPY$SEX, (HAPPY$SEX == "IAP"), NA)
HAPPY$SEX <- replace(HAPPY$SEX, (HAPPY$SEX == "DK"), NA)
HAPPY$SEX <- replace(HAPPY$SEX, (HAPPY$SEX == "NA"), NA)
# SET TYPES
HAPPY$SEX <- as.factor(HAPPY$SEX)
```
```{r}
HAPPY$MARITAL <- replace(HAPPY$MARITAL, (HAPPY$MARITAL == "IAP"), NA)
HAPPY$MARITAL <- replace(HAPPY$MARITAL, (HAPPY$MARITAL == "DK"), NA)
HAPPY$MARITAL <- replace(HAPPY$MARITAL, (HAPPY$MARITAL == "NA"), NA)
# SET TYPES
HAPPY$MARITAL <- as.factor(HAPPY$MARITAL)
```
```{r}
HAPPY$DEGREE <- replace(HAPPY$DEGREE, (HAPPY$DEGREE == "IAP"), NA)
HAPPY$DEGREE <- replace(HAPPY$DEGREE, (HAPPY$DEGREE == "DK"), NA)
HAPPY$DEGREE <- replace(HAPPY$DEGREE, (HAPPY$DEGREE == "NA"), NA)
# SET TYPES
HAPPY$DEGREE <- as.factor(HAPPY$DEGREE)
```
```{r}
# Set NULLS
HAPPY$FINRELA <- replace(HAPPY$FINRELA, (HAPPY$FINRELA == "IAP"), NA)
HAPPY$FINRELA <- replace(HAPPY$FINRELA, (HAPPY$FINRELA == "DK"), NA)
HAPPY$FINRELA <- replace(HAPPY$FINRELA, (HAPPY$FINRELA == "NA"), NA)
# SET TYPES
HAPPY$FINRELA <- as.factor(HAPPY$FINRELA)
# SET FACTOR ORDER
HAPPY$FINRELA <- factor(HAPPY$FINRELA, levels = c("FAR BELOW AVERAGE", "BELOW AVERAGE", "AVERAGE", "ABOVE AVERAGE", "FAR ABOVE AVERAGE"))
```
```{r}
# Set NULLS
HAPPY$HEALTH <- replace(HAPPY$HEALTH, (HAPPY$HEALTH == "IAP"), NA)
HAPPY$HEALTH <- replace(HAPPY$HEALTH, (HAPPY$HEALTH == "DK"), NA)
HAPPY$HEALTH <- replace(HAPPY$HEALTH, (HAPPY$HEALTH == "NA"), NA)
# SET TYPES
HAPPY$HEALTH <- as.factor(HAPPY$HEALTH)
# SET FACTOR ORDER
HAPPY$HEALTH <- factor(HAPPY$HEALTH, levels = c("POOR", "FAIR", "GOOD", "EXCELLENT"))
```
```{r}
# SET NULLS
HAPPY$WTSSALL <- replace(HAPPY$WTSSALL, (HAPPY$WTSSALL == "IAP"), NA)
HAPPY$WTSSALL <- replace(HAPPY$WTSSALL, (HAPPY$WTSSALL == "AGE"), NA)
HAPPY$WTSSALL <- replace(HAPPY$WTSSALL, (HAPPY$WTSSALL == "AGE"), NA)
# SET TYPES
HAPPY$WTSSALL <- as.numeric(HAPPY$WTSSALL)
```

# Part Two:
___
```{r}
ggplot(HAPPY, aes(x = MARITAL, fill = SEX)) +
  geom_bar(position = "fill") +
  labs(x = "Marital status", y = "Proportion", fill = "Sex") +
  theme_bw()
```
```{r}
ggplot(HAPPY) +
  geom_bar(aes(x=SEX, fill=MARITAL),
           position = "dodge") +
  facet_wrap(~HAPPY)
```
The above plot shows the relation between Sex and Marital status between the different Happiness categories. It shows that the largest frequencies occur in married people, who are usually pretty and very happy. Those who are not too happy show little relative variation between marital states. This shows that when people are married they are more likely to be married.
# Individual Question: Ahmed Gharib
___
### Is there a relation between age and Marital states?
```{r}
ggplot(HAPPY) +
  geom_bar(aes(x=AGE, fill= MARITAL),
           position = "dodge") +
  facet_wrap(~MARITAL)
```
